### 2024-05-16 Answer to referee/answer-to-referee.tex

			\item Done.
			\item Done.
			\item Fixed, the index is now $A$.
			\item Done, probably the referee was confused by the fact that we use (4.4.37) in the third and not in the second equality. We clarified which equations are used. 

@@

		\end{enumerate}
\section*{Further corrections}
\begin{enumerate}
\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (5.2.10) in the arxiv version of the paper. 
\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they where before. Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorbe particles, not the holes. 
\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the mixed moments in the non-equilibrium steady state. I have fixed equation (5.1.3) and above and I have added Remark 13 to clarify.

### 2024-05-16 main.tex
jkl

where in the second equality we used \eqref{usefulRelaton-many}. 

@@

{As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e. the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}. }

@@

The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
\begin{equation}
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
\end{equation}
where $C(\nu,m)$ is a constant that depends on $m$ and {\color{black} on the maximal occupancy} per site $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state. The following equalities hold using ergodicity and duality:
\begin{equation}\label{ExptationSS}
	\begin{split}
		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\\&=
		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\fra{\sum_{s_{N-1}=0}^{|\xi_{N-1}|}}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}
	\end{split}
\end{equation}
here we recall that, generalizing Corollary~\ref{Corolollary-ABS_Corr-abstract},
\begin{equation}\label{Pass} 
\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $s_{a}$ particles of species $a$ are absorbed at $0$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one-point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. 
 The absorption probabilities for higher point correlations fulfil  difference equations.
  \begin{remark}
	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the $m$-mixed factorial moments under the non-equilibrium stationary distribution.}
\end{remark}

>>>>

where in the second equality \fra{we used \eqref{commLEFT} and in the third equality we used  \eqref{usefulRelaton-many}}. 

@@

{As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, %i.e. the situation where the process has only one species of particles and holes, 
with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}. \fra{[Words removed for point 33]}}

@@

The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
\begin{equation}
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
\end{equation}
where $C(\nu,m)$ is a constant that depends on $m$ and {\color{black} on the maximal occupancy} per site $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state. The following equalities hold using ergodicity and duality:
\begin{equation}\label{ExptationSS}
	\begin{split}
		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\\&=
		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\fra{\sum_{s_{N-1}=0}^{|\xi_{N-1}|}}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}
	\end{split}
\end{equation}
here we recall that, generalizing Corollary~\ref{Corolollary-ABS_Corr-abstract},
\begin{equation}\label{Pass} 
\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $s_{a}$ particles of species $a$ are absorbed at $0$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one-point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. 
 The absorption probabilities for higher point correlations fulfil  difference equations.
  \begin{remark}
	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the mixed factorial moments under the non-equilibrium stationary distribution.}
\end{remark}
